---
title: "Chapter 01: R Intro"
author: "蔡有為"
date: "2015年7月8日"
output: html_document
---
##What is R?##
1. R in Wikipedia: <https://zh.wikipedia.org/wiki/R%E8%AF%AD%E8%A8%80>
2. What is R?: <http://www.r-project.org/about.html> / <http://www.revolutionanalytics.com/what-r>
3. R Consortium: <http://www.linuxfoundation.org/news-media/announcements/2015/06/linux-foundation-announces-r-consortium-support-millions-users>
4. R at Microsoft: <http://www.slideshare.net/RevolutionAnalytics/r-at-microsoft>

##R的學習資源##
1. 中華R軟體學會: <http://www.r-software.org/home/learn>
2. Taiwan R User Group(每周一晚上有MLDM Monday聚會): <http://www.meetup.com/Taiwan-R/>
3. R軟體使用者論壇: <https://groups.google.com/forum/#!forum/taiwanruser>
4. Youtube R演習室: <https://www.youtube.com/watch?v=STcIxf_vUWY&list=PL5AC0ADBF65924EAD>
5. 金門大學陳鍾誠老師R教材: <http://ccckmit.wikidot.com/r:main> / <http://ccckmit.wikidot.com/st:main>
6. DataCamp - Introduction to R: <https://www.datacamp.com/courses/free-introduction-to-r>
7. Code School - Try R: <http://tryr.codeschool.com>
8. 台大資訊系統訓練班 - R 程式設計班: <https://www.csie.ntu.edu.tw/train/?page=course_info.html&courseid=1239>
9. 30 天精通 Git 版本控管: <https://github.com/doggy8088/Learn-Git-in-30-days>

##R軟體下載##
1. 下載Revolution R Open: <http://mran.revolutionanalytics.com/download/#download> (both Software & Math Library)
2. 下載R Studio: <https://www.rstudio.com/products/rstudio/download>
3. 下載GitHub Desktop(optional): <https://windows.github.com> or <https://mac.github.com>

##安裝後的簡單測試##
```{r}
summary(cars)
```

You can also embed plots, for example:

```{r}
plot(cars)
```
